Publication Ready

### 2022-09-27 Publication_Ready.Rmd
For the existing results add prediction accuracy

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_VAR<-All_VAR

@@

All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])

All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"

Final_Data_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                               cbind.data.frame(Metric="EMSE",All_EMSE),
                               cbind.data.frame(Metric="Model Information",All_Info),
                               cbind.data.frame(Metric="MSE",All_MSE),
                               cbind.data.frame(Metric="Variance",All_VAR))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR)
```

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

@@

@@

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
               OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
               OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
               OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
               OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])

@@

ggarrange(p1,p2,p3,p4,nrow = 4)
```

@@

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p4_New
```

```{r All Plots}
ggarrange(p1,p1_New,
          p2,p2_New,nrow = 4)
```

>>>>

for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i]] <-paste0("RS ",New_Labels[i])
}

RS_Bias<-All_Bias 
RS_EMSE<-All_EMSE
RS_Info<-All_Info
RS_MSE<-All_MSE
RS_VAR<-All_VAR
RS_ACC<-Accuracy_Data

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

@@

All_Bias<-All_Bias[!(All_Bias$Model %in% remove_stuff),]
All_EMSE<-All_EMSE[!(All_EMSE$Model %in% remove_stuff),]
All_MSE<-All_MSE[!(All_MSE$Model %in% remove_stuff),]
All_Info<-All_Info[!(All_Info$Model %in% remove_stuff),]
All_VAR<-All_VAR[!(All_VAR$Model %in% remove_stuff),]
Accuracy_Data<-Accuracy_Data[!(Accuracy_Data$Model %in% remove_stuff),]

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
                OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
                OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
                OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")])
All_ACC<-rbind(RS_ACC,
                OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
                OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")])
All_Objects<-ls()
remove(list = All_Objects[startsWith(All_Objects,"OSMAC")])

colnames(All_Bias)[3]<-"Estimated Values"
colnames(All_EMSE)[3]<-"Estimated Values"
colnames(All_Info)[3]<-"Estimated Values"
colnames(All_MSE)[3]<-"Estimated Values"
colnames(All_VAR)[3]<-"Estimated Values"
colnames(All_ACC)[3]<-"Estimated Values"

Final_Data_Identical_r0<-rbind(cbind.data.frame(Metric="Bias",All_Bias),
                               cbind.data.frame(Metric="EMSE",All_EMSE),
                               cbind.data.frame(Metric="Model Information",All_Info),
                               cbind.data.frame(Metric="MSE",All_MSE),
                               cbind.data.frame(Metric="Variance",All_VAR),
                               cbind.data.frame(Metric="Accuracy",All_ACC))

remove(All_Bias,All_EMSE,All_Info,All_MSE,All_VAR,All_ACC)
```

@@

## mMSE
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE ",New_Labels[i])
}

OSMAC_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
for (i in 1:length(Old_Labels)) 
{
  All_Bias$Model[All_Bias$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_EMSE$Model[All_EMSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_Info$Model[All_Info$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_MSE$Model[All_MSE$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  All_VAR$Model[All_VAR$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
  Accuracy_Data$Model[Accuracy_Data$Model==Old_Labels[i] & All_Bias$Type == "mVc"] <-paste0("OSMAC mVc ",New_Labels[i])
}

OSMAC_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

@@

Accuracy_Data<-cbind(Model="Real Model",Accuracy_Data)

@@

All_Bias<-All_Bias[All_Bias$Model==Old_Labels[1],]
All_EMSE<-All_EMSE[All_EMSE$Model==Old_Labels[1],]
All_Info<-All_Info[All_Info$Model==Old_Labels[1],]
All_MSE<-All_MSE[All_MSE$Model==Old_Labels[1],]
All_VAR<-All_VAR[All_VAR$Model==Old_Labels[1],]
Accuracy_Data<-Accuracy_Data[Accuracy_Data$Model==Old_Labels[1],]

## mMSE
All_Bias$Model[All_Bias$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_EMSE$Model[All_EMSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_Info$Model[All_Info$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_MSE$Model[All_MSE$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
All_VAR$Model[All_VAR$Type == "mMSE"] <-paste0("OSMAC mMSE MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mMSE"] <-paste0("OSMAC mMSE MF")

OSMAC_MF_mMSE_Bias<-All_Bias[All_Bias$Type == "mMSE",] 
OSMAC_MF_mMSE_EMSE<-All_EMSE[All_EMSE$Type == "mMSE",]
OSMAC_MF_mMSE_Info<-All_Info[All_Info$Type == "mMSE",]
OSMAC_MF_mMSE_MSE<-All_MSE[All_MSE$Type == "mMSE",]
OSMAC_MF_mMSE_VAR<-All_VAR[All_VAR$Type == "mMSE",]
OSMAC_MF_mMSE_ACC<-Accuracy_Data[Accuracy_Data$Type == "mMSE",]

## mVc
All_Bias$Model[All_Bias$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_EMSE$Model[All_EMSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_Info$Model[All_Info$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_MSE$Model[All_MSE$Type == "mVc"] <-paste0("OSMAC mVc MF")
All_VAR$Model[All_VAR$Type == "mVc"] <-paste0("OSMAC mVc MF")
Accuracy_Data$Model[Accuracy_Data$Type == "mVc"] <-paste0("OSMAC mVc MF")

OSMAC_MF_mVc_Bias<-All_Bias[All_Bias$Type == "mVc",] 
OSMAC_MF_mVc_EMSE<-All_EMSE[All_EMSE$Type == "mVc",]
OSMAC_MF_mVc_Info<-All_Info[All_Info$Type == "mVc",]
OSMAC_MF_mVc_MSE<-All_MSE[All_MSE$Type == "mVc",]
OSMAC_MF_mVc_VAR<-All_VAR[All_VAR$Type == "mVc",]
OSMAC_MF_mVc_ACC<-Accuracy_Data[Accuracy_Data$Type == "mVc",]

remove(All_Bias,All_EMSE,All_MSE,All_Info,All_VAR,Accuracy_Data)

# All elements
All_Bias<-rbind(RS_Bias,
                OSMAC_mMSE_Bias[,!(colnames(OSMAC_mMSE_Bias) %in% "Type")],
                OSMAC_mVc_Bias[,!(colnames(OSMAC_mVc_Bias) %in% "Type")],
                OSMAC_MF_mMSE_Bias[,!(colnames(OSMAC_MF_mMSE_Bias) %in% "Type")],
                OSMAC_MF_mVc_Bias[,!(colnames(OSMAC_MF_mVc_Bias) %in% "Type")])
All_EMSE<-rbind(RS_EMSE,
                OSMAC_mMSE_EMSE[,!(colnames(OSMAC_mMSE_EMSE) %in% "Type")],
                OSMAC_mVc_EMSE[,!(colnames(OSMAC_mVc_EMSE) %in% "Type")],
                OSMAC_MF_mMSE_EMSE[,!(colnames(OSMAC_MF_mMSE_EMSE) %in% "Type")],
                OSMAC_MF_mVc_EMSE[,!(colnames(OSMAC_MF_mVc_EMSE) %in% "Type")])
All_MSE<-rbind(RS_MSE,
               OSMAC_mMSE_MSE[,!(colnames(OSMAC_mMSE_MSE) %in% "Type")],
                OSMAC_mVc_MSE[,!(colnames(OSMAC_mVc_MSE) %in% "Type")],
                OSMAC_MF_mMSE_MSE[,!(colnames(OSMAC_MF_mMSE_MSE) %in% "Type")],
                OSMAC_MF_mVc_MSE[,!(colnames(OSMAC_MF_mVc_MSE) %in% "Type")])
All_Info<-rbind(RS_Info,
                OSMAC_mMSE_Info[,!(colnames(OSMAC_mMSE_Info) %in% "Type")],
                OSMAC_mVc_Info[,!(colnames(OSMAC_mVc_Info) %in% "Type")],
                OSMAC_MF_mMSE_Info[,!(colnames(OSMAC_MF_mMSE_Info) %in% "Type")],
                OSMAC_MF_mVc_Info[,!(colnames(OSMAC_MF_mVc_Info) %in% "Type")])
All_VAR<-rbind(RS_VAR,
               OSMAC_mMSE_VAR[,!(colnames(OSMAC_mMSE_VAR) %in% "Type")],
               OSMAC_mVc_VAR[,!(colnames(OSMAC_mVc_VAR) %in% "Type")],
               OSMAC_MF_mMSE_VAR[,!(colnames(OSMAC_MF_mMSE_VAR) %in% "Type")],
               OSMAC_MF_mVc_VAR[,!(colnames(OSMAC_MF_mVc_VAR) %in% "Type")])
All_ACC<-rbind(RS_ACC,
               OSMAC_mMSE_ACC[,!(colnames(OSMAC_mMSE_ACC) %in% "Type")],
               OSMAC_mVc_ACC[,!(colnames(OSMAC_mVc_ACC) %in% "Type")],
               OSMAC_MF_mMSE_ACC[,!(colnames(OSMAC_MF_mMSE_ACC) %in% "Type")],
               OSMAC_MF_mVc_ACC[,!(colnames(OSMAC_MF_mVc_ACC) %in% "Type")])

@@

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Accuracy"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average Accuracy",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p5

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Accuracy"),] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+
  scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average_Accuracy",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data,scales = "free_y")->p6

ggarrange(p1,p2,p3,p4,nrow = 4)
ggarrange(p5,p6,nrow = 2)
```

@@

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Model Information") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Estimated Model Information",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p4_New

Final_Data[(Final_Data$Model %in% Selected_mMSE) & (Final_Data$Metric == "Accuracy") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average Accuracy",subtitle = "mMSE")+
  ylab("Estimated Values")+facet_wrap(~Data)->p5_New

Final_Data[(Final_Data$Model %in% Selected_mVc) & (Final_Data$Metric == "Accuracy") & 
             Final_Data$Subsample_Size %in% SS_Choice,] %>%
  ggplot(.,aes(x=Subsample_Size,y=`Estimated Values`,color=Model))+
  geom_point(size=1.75)+geom_line(size=1)+scale_color_manual(values=Colors_mMSE)+
  theme_light()+xlab("Sub sample size")+
  ggtitle("Comparing Average Accuracy",subtitle = "mVc")+
  ylab("Estimated Values")+facet_wrap(~Data)->p6_New
```

```{r All Plots}
ggarrange(p1,p1_New,
          p2,p2_New,nrow = 4)

ggarrange(p5_New,p6_New,nrow = 2)
```
